%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 1}
\problem{1}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P1}

A monoenergetic muon beam is produced at point $A$ and directed to point $B$, which is 20 km away. Suppose that only 2/3 of the muons reach point $B$ and the remainder decay in flight. Find the energy of the muons. In the rest frame of a muon, its mass and lifetime are 105.7 MeV/$c^2$ and $2.2\times10^{-6}$ s, respectively.

\subsubsection{Answer}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 2}
\problem{2}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P2}
A wheel consists of a thin cylindrical steel shell of radius $R$, mass $M$, and density $\rho$ mounted on light but very strong spokes. The wheel rotates around a vertical axle, which coincides with its axis of symmetry, and is used to store energy.
\begin{enumerate}
	\item Find the stress in the steel shell when the angular speed of rotation is $\omega$.
	\item If steel breaks apart when the stress reaches $3\times10^8$ N/m$^2$ , what is the maximum energy that can be stored per unit volume?
\end{enumerate}

\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 3
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 3}
\problem{3}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P3}
Suppose that Chicago and Minneapolis are connected by an underground train that is confined to run on a straight track of 600 km between the two cities. The train is released from rest at either city and powered solely by gravity (ignore all dissipative forces). Ignore the rotation of the earth and assume that it is a uniform sphere of $6\times10^24$ kg in mass and 6400 km in radius. How long does a one-way trip last and what is the maximum speed of the train?
\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 4
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 4}
\problem{4}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P4}
A long cylindrical capacitor has an inner cylinder of adjustable radius and a thin outer cylindrical shell of fixed radius $b$. The inner cylinder is at a fixed potential $V$ and the outer shell is at a fixed zero potential. You need to adjust the radius of the inner cylinder so as to minimize the electric field at the surface of the inner cylinder. Find this radius $R_{in}$ of the inner cylinder.
\subsubsection{Answer}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 5
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 5}
\problem{5}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P5}
A parallel-plate capacitor has two plates each of area $A$ and is connected to a battery of voltage $V$ . The initial separation between the two plates is $d$.
\begin{enumerate}
	\item If one plate is fixed and the other is moved by an external force to double the separation, what is the work done by the external force?
	\item Show that the work in (1) equals the net change of energy in the battery-capacitor system.
\end{enumerate}
 
\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 6
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 6}
\problem{6}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P6}
A non-relativistic particle of mass $m$ is in the potential $V(x) = -\alpha\delta(x)$ with $\alpha> 0$. How many bound states are there? Find the energy eigenvalue and the expectation value of $x^2$ for each bound state.
\subsubsection{Answer}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 7
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 7}
\problem{7}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P7}
The sun radiates photons at a total power of $4\times10^26$ Watts, which is supplied by a series of reactions effectively converting four protons into a ${}^4$He nucleus.
\begin{enumerate}
	\item Write down the effective net reaction of converting four protons into a 4 He nucleus by considering conservation laws.
	\item By using the values of the particle masses provided on the cover sheet, estimate the total number of neutrinos emitted by the sun per second.
\end{enumerate}
\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 8
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 8}
\problem{8}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P8}
The speed of sound in a gas is $v = \sqrt{(\partial P/\partial \rho)_S}$, where $P$, $\rho$, and $S$ are the pressure, mass density, and entropy of the gas, respectively. A standing sound wave forms in a tube filled with iodine vapor (an ideal gas) at 400 K. The frequency of the wave is 1000 Hz and the distance between the adjacent nodes is 6.77 cm. Determine whether iodine vapor is a monoatomic or diatomic gas. The atomic weight of iodine is 127.
\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 9
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 9}
\problem{9}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P9}
Derive the relation between the pressure and energy density of black-body radiation. You may do this by considering the collisions of photons with the wall of a cavity enclosing such radiation, or by any other way that you may choose.
\subsubsection{Answer}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Problem 10
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Problem 10}
\problem{10}
\subsubsection{Question}
% Keywords
	\index{unsolved!Spring 2011 I.P10}
A windmill has blades of 15 meters in diameter. If the wind is blowing into the windmill at a speed of 12 m/s and the downstream air moves at a speed of 10 m/s, estimate the power generated by the windmill. The density of air blown into the windmill is 1.3 kg/m$^3$ .
\subsubsection{Answer}

